Uncovering underlying high-level musical content in the temporal domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music embeddings with applications to MIR downstream tasks

### 2023-05-26 figures/neural networks/Back_propagation.tex
Updates from Overleaf

		\draw[->,red,line width=0.05cm] (2,-0.25) -- (0.75,0.3);
		\draw[->,red,line width=0.05cm] (2,2) -- (0.75,1.6);
    	\end{tikzpicture}
	\caption[Backpropagation.]{\small{Backpropagation of errors through the network: once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backward.}}
	\label{fig:error-backpropagation}
\end{SCfigure}

>>>>

		\draw[->,red,line width=0.05cm] (2,-0.25) -- (0.75,0.3);
		\draw[->,red,line width=0.05cm] (2,2) -- (0.75,1.6);
    	\end{tikzpicture}
	\caption[Backpropagation.]{\small{Backpropagation of errors through the network; once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backward.}}
	\label{fig:error-backpropagation}
\end{SCfigure}

### 2023-05-26 introduction/Subsections/Previous work.tex
Updates from Overleaf

Neural networks have recently facilitated the development of low-dimensional embeddings that capture essential musical features, enabling the computation of various task-specific aspects. These aspects include:

\begin{itemize}

\item The utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}.

\item The enhancement of environmental sound classification \cite{Kim2020OneStrategies}.

\item The improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}.

\item The enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}.

\item The creation of a music similarity search engine specifically for video producers \cite{epidemic}.

\item The improved performance in Music Emotion Recognition (MER) tasks, eliminating the necessity for expert human engineering \cite{KohComparisonRecognition}.

\item The resolution of the cross-modal text-to-music retrieval problem, enabling content creators to find music that matches the emotion conveyed in their text-based stories \cite{WonEmotionStories}.

\item Music rearrangement is traditionally undertaken by expert music engineers or more classical MIR approaches \cite{Stoller2018IntuitiveTransitions}. This innovative approach presents a promising avenue for automated music rearrangement, enhancing the process's efficiency and quality. \cite{Plachouras2023MusicSegmentation}

\end{itemize}

>>>>

Neural networks have recently facilitated the development of low-dimensional embeddings that capture essential musical features, enabling the computation of various task-specific aspects.

These aspects include the utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}, the enhancement of environmental sound classification \cite{Kim2020OneStrategies}, the improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}, the enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}, the creation of a music similarity search engine specifically for video producers \cite{epidemic}, the improved performance in Music Emotion Recognition (MER) tasks \cite{KohComparisonRecognition}, embedding songs for similarity comparison based on artist identification \cite{contentmusicsimtriplet2020}, the resolution of the cross-modal text-to-music retrieval problem \cite{WonEmotionStories}, and music rearrangement \cite{Stoller2018IntuitiveTransitions}. This last innovative approach presents a promising avenue for automated music rearrangement, enhancing the process's efficiency and quality \cite{Plachouras2023MusicSegmentation}.

### 2023-05-26 methods/subsections/implementation.tex
Updates from Overleaf

The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel. The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels. It is followed by batch normalization and ReLU activation.

@@

In this equation, the triplet loss function with a variable margin:

@@

The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances \cite{XuanImprovedMining}.

@@

\begin{figure}
    \centering
    \includegraphics[clip,width=\columnwidth]{figures/images/Triplet Network.jpeg}
    \caption[]{Caption}
    \label{fig:my_label}
\end{figure}

>>>>

The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel and follows the next architecture:

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{|>{\hsize=1.6\hsize}X|>{\hsize=0.6\hsize}X|>{\hsize=0.6\hsize}X|}
\hline
\textbf{Layer Type} & \textbf{In Channels} & \textbf{Out Channels} \\
\hline
Conv1d + BatchNorm1d + ReLU & 1 & 128 \\
\hline
\multicolumn{3}{|c|}{The following layers are repeated depending on the strides and hidden parameters} \\
\hline
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 128 \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 128 \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 256 \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 512 \\
\hline
Conv1d + BatchNorm1d + ReLU & 512 & 512 \\
\hline
Fully connected representation layer & 512 & 128 \\
\hline
\end{tabularx}
\caption{Layer specifications for SampleCNN model}
\label{tab:samplecnn}
\end{table}

@@

@@

The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances \cite{Sikaroudi2020OfflinePatches}\cite{XuanImprovedMining}.

@@

\begin{equation}
L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
\end{equation}
\newpage
